The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-02-15 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Changed paragraph on WISE colours

The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with
(W1-W2) = --0.458 (i.e. 0.154 in Vega), and the WISE W1W2W3 color image
is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}. The reddest object in
(W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 0.719 (1.33 Vega).

>>>>

The VH$z$Q with the bluest colour in (W1-W2) is SDSS~J0927+2001, with
(W1-W2) = --0.283 (i.e. 0.328 in Vega), and the WISE W1W2W3 color image
is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}. The reddest object in
(W1-W2) is PSO~J135.3860+16.2518 with (W1-W2) = 0.721 (1.33
Vega).
